---
title: "simpleRegress"
author: "Jayline Zelaya"
date: "Fall 2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
#adjust factors to be factors
bears$SEX<- as.factor(bears$SEX)
bears$MONTH<- as.factor(bears$MONTH)
```

## Model LENGTH ~ NECK  this is an example  

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```


## Compare all models that predict LENGTH other than NECK. Then order them from worst to best by its value of Adjusted-Rsquared (bigger is better), or by RSE (residual standard error) where smaller is better. 

## make a regression model for age


## Model LENGTH ~ AGE  this is an example  

```{r}
AGEMODEL <- lm(LENGTH~AGE,data=bears)
plot(LENGTH~NECK,data=bears)
abline(AGEMODEL)
summary.lm(AGEMODEL)
```



## make a regression model for HEAD


## Model LENGTH ~ HEAD  this is an example  

```{r}
HEADLEN <- lm(LENGTH~HEADLEN,data=bears)
plot(LENGTH~HEADLEN,data=bears)
abline(HEADLEN)
summary.lm(HEADLEN)
```


## make a regression model for HEADWTH


## Model LENGTH ~ HEADWTH  this is an example  

```{r}
HEADWTH <- lm(LENGTH~HEADWTH,data=bears)
plot(LENGTH~HEADWTH,data=bears)
abline(HEADWTH)
summary.lm(HEADWTH)
```

## make a regression model for CHEST


## Model LENGTH ~ CHEST  this is an example  

```{r}
CHEST <- lm(LENGTH~CHEST,data=bears)
plot(LENGTH~CHEST,data=bears)
abline(CHEST)
summary.lm(CHEST)
```


## make a regression model for WEIGHT


## Model LENGTH ~ WEIGHT  this is an example  

```{r}
WEIGHT <- lm(LENGTH~WEIGHT,data=bears)
plot(LENGTH~WEIGHT,data=bears)
abline(WEIGHT)
summary.lm(WEIGHT)
```



## CONCLUSION

of all the models the best is HEADLEN because the adjusted r squared value is 0.8434 which is also the highest
